### 2014-03-02 paper/concrete.tex
Fix notation in concrete.

  \begin{mathpar}
    \inferrule[C-fork]
    {
      \text{|ie| does not contain any |ta|}\\
      |iS' = bracket iS (mapsto id' nil)|\\
      |it1 = oneheapfullconf id il (iniE id')|\\
      |itnew = oneheapfullconf id' il (TI ie)|\\
      |fresh (id')|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (fork ie)), ldots)
      .->
      iS'; tS; sched F (it1, ldots, itnew)
    |}
    \and
    \inferrule[C-send]
    {
      \text{|ie| does not contain any |ta|}\\
      |il canFlowTo il'|\\
      |iS(id') = Q|\\
      |iS' = bracket iS (mapsto id' (il', id,  ie) , Q)|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' ie)), ldots)
      ->
      iS; tS; sched step (oneheapfullconf id il unit, ldots)
    |}
  \end{mathpar}

>>>>

  \begin{mathpar}
    \inferrule[C-fork]
    {
      \text{|ie| does not contain any |ta|}\\
      |iS' = bracket iS (mapsto id' nil)|\\
      |it1 = oneheapfullconf id il (iniE id')|\\
      |itnew = oneheapfullconf id' il (TI ie)|\\
      |fresh (id')|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id1 il1 (iniEi (fork ie)), ldots)
      .->
      iS'; tS; sched F (it1, ldots, itnew)
    |}
    \and
    \inferrule[C-send]
    {
      \text{|ie| does not contain any |ta|}\\
      |canFlowTo2 il il'|\\
      |iS(id') = Q|\\
      |iS' = bracket iS (mapsto id' (il', id,  ie) , Q)|
    }
    {|
      oneheapiconf iS tS (oneheapfullconf id il (iniEi (send id' il' ie)), ldots)
      ->
      iS; tS; sched step (oneheapfullconf id il unit, ldots)
    |}
  \end{mathpar}
